\documentclass[thesis=M,english,hidelinks]{inc/FITthesis}[2012/10/20]

\usepackage[utf8]{inputenc}

\usepackage{graphicx}
\usepackage{dirtree}
\usepackage{booktabs}
\usepackage{listings,xcolor}

\input{inc/golang.tex}
\input{inc/yaml.tex}
\input{inc/dockerfile.tex}

\department{Department of Software Engineering}
\title{Suitability analysis of Kubernetes for~Seznam.cz}
\authorGN{Ondřej}
\authorFN{Šejvl}
\author{Ondřej Šejvl}
\authorWithDegrees{Bc. Ondřej Šejvl}
\supervisor{Ing. Jan Baier}

\acknowledgements{Most of all I~would like to thank to my thesis advisor Ing.~Jan Baier for his expert guidance and invaluable remarks. I~would also like to thank to Ing.~Tomáš Kukrál for his counsel during my work and for a lot of open source material.

To the Seznam.cz company and to my team leader David Bouček in particular, I~thank for providing me with hardware, introducing me to technologies like Kubernetes and Docker, letting me dedicate a part of my working time to this thesis and constantly bringing in fresh ideas for improvements.

My thanks belong to Martin Stružský for the proofreading as well.

And of course, this thesis wouldn't have been possible without the support of my family, especially my wife.}

\abstractEN{This thesis analyses the suitability of the Kubernetes system in the Seznam.cz’s company environment. The first part of the thesis focuses on the theory and identifies possible problems connected with a switch to this technology. The second part of the thesis describes solving those problems and running the cluster together with other applications.}

\abstractCS{Tato práce analyzuje použitelnost systému Kubernetes v~prostředí společnosti Seznam.cz. V~první části je práce zaměřena na teoretické informace a jsou zde identifikovány možné problémy spojené s~přechodem na tuto technologii. V~druhé části se práce zabývá vyřešením těchto problémů a zprovozněním clusteru s~dalšími podpůrnými aplikacemi.}

\placeForDeclarationOfAuthenticity{Prague}

\keywordsCS{Kubernetes, Seznam.cz, Docker, Heka, Kafka, Linux, virtualizace}
\keywordsEN{Kubernetes, Seznam.cz, Docker, Heka, Kafka, Linux, virtualization}

\declarationOfAuthenticityOption{5} 
\website{https://github.com/sejvlond/master-thesis}

\begin{document}
\nocite{*}

\setsecnumdepth{part}
\input{chapters/introduction}

\setsecnumdepth{all}

\include{chapters/seznam-nowadays}
\include{chapters/what-is-kubernetes}
\include{chapters/what-is-docker}
\include{chapters/kubernetes-basic-concepts}
\include{chapters/kubernetes-architecture}
\include{chapters/possible-problems-with-kubernetes-in-seznam-cz}
\include{chapters/running-kubernetes}
\include{chapters/docker-registry}
\include{chapters/secrets-distribution}
\include{chapters/logging}
\include{chapters/security}
\include{chapters/monitoring}
\include{chapters/static-webpages-content}
\include{chapters/testing-application}
\include{chapters/testing-the-cluster}
\include{chapters/benchmarking-python-and-go-application-servers}
\include{chapters/benefits-for-seznam}

\setsecnumdepth{part}
\include{chapters/conclusion}

\bibliographystyle{inc/iso690}
\bibliography{bibliography}

\setsecnumdepth{all}
\appendix

\include{appendix/acronyms}

\include{appendix/cd-contents}

\end{document}